



In this section we provide some interesting results for ASGs that 
we have built using Hylian.
Table \ref{tab:asgstats} summarizes these results for three
programs in our test suite: a {\sf Hello World} program written in
C and {\CPP}, and {\sf AlephOne}, a rather large
video game translated into {\CPP} that uses the
Simple Direct Media Layer (SDL) API, as well as the Lua
embedded scripting engine.
There are two sections of data in the table: the top section 
that summarizes results for the construction of {\sf Parse Trees}, 
and the bottom section that summarizes results for the construction
of ASGs. We are comparing parse trees and ASGs in the top and bottom
sections to show the reduction in the size of ASGs compared to parse
trees, and the reduction in size when the ASGs for each compilation 
unit in a program are {\em linked}, or merged,
into a single ASG for the entire program.


To evaluate the results, we first consider the data
for the three ``Hello World'' programs.
The first column in the table describes the information in the particular
row of the table, and the next three columns represent information
for the ``Hello World'' programs written in C and {\CPP}.
Our first result shows that both the C and {\CPP}
versions of ``Hello World'' consist of a single {\sf Compilation Unit},
as shown by the first row of data in the table for columns two, three
and four; however, the {\sf No. System Terminals} in the C version has
2,930 terminals in the parse trees, but the {\CPP} versions have 132,122
terminals in their parse trees, so that the {\CPP} version has almost
two orders of magnitude more terminals than the C version. This
differential is caused by the inclusion of {\sf iostream} and much
of the {\CPP} library in the {\CPP} version of ``Hello World.''
Also, the {\sf No. System Terminals} in the {\sf AlephOne} program
is 30,339,853 (first row, last column of the table), 
illustrating the large number of system terminals
needed for a standard video game. The remaining rows at the top
of the Table \ref{tab:asgstats} reflect similar comparisons.

The bottom section of Table \ref{tab:asgstats} summarizes results
for the ASGs that Hylian builds. The second and third columns in
the bottom section compare the ASG for a full parse of a C and
a {\CPP} ``Hello World'' program. For example, the third row of
the bottom section of the table shows that there are 984 vertices
in the C version, and 21,861 vertices in the {\CPP} version, an
order of magnitude increase. Since there is only one compilation
unit in each ``Hello World'' program, there are is only one ASG
and therefore no vertices are linked; thus, the second and fourth
rows in the bottom section of the table do not list any values
for {\sf No. Vertices (linked)} or {\sf No. Edges (linked)}.


